The \dealii Library, Version 9.5

### 2023-06-24 9.5/paper.tex
shift text below cpp code to avoid confusion

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on \texttt{parallel::distributed::Triangulation} objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose we introduce a free function that computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector indicating entities of a given triangulation (in the form of \texttt{GridTools::Cache}) that intersections are computed upon.
Each entity (face or cell) is described by a vector of vertices. The actual computation of the intersection of two geometric
entities is performed by the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()}.

\todo[inline]{The following code snippet uses a different function
  that the text above. The connection between the two is not clear to me.}

@@

>>>>

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on \texttt{parallel::distributed::Triangulation} objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose we introduce a free function that computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector indicating entities of a given triangulation (in the form of \texttt{GridTools::Cache}) that intersections are computed upon.
Each entity (face or cell) is described by a vector of vertices.

@@

Internally above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()}, to actually compute intersections between two geometric entities.
